Estimating duration using survival analysis

### 2024-03-29 cis-perfect-testing.tex
add figure for new likelihood

Let $n_k$ denote the number of observations of $\vec{\nu}_k$; $\nnodet$ denote the latent number of undetected episodes; and $\vec{n} = [n_1, \dots, n_{N_D}, \nnodet]^T$.
Hence, $\ntot = \sum_{i=1}^{N_D} n_i + \nnodet$.
For $\vec{\nu}_k \in \set{E}$, let $p_k = \prob(O(j) = \vec{\nu}_k \mid \vec{\theta})$; $p_u = \prob(O(j) = \emptyset \mid \vec{\theta})$; and $\vec{p} = [p_1, \dots, p_D, p_u]^T$.
Assume, for tractability, that the events $O(j) = \vec{\nu}_k$ and $O(j') = \vec{\nu}_{k'}$ are independent for $j \neq j'$; this assumption is discussed in \cref{perf-test:sec:discussion}.
Then:
\begin{align}
  \vec{n} \mid \ntot, \vec{\theta} &\dist \MN(\ntot, \vec{p})
\intertext{that is:}
  p(\vec{n} \mid \ntot, \vec{\theta}) &= \frac{\ntot!}{\nnodet!\prod_{k=1}^{N_D} n_k!} p_u^{\nnodet} \prod_{k=1}^{N_D} p_k^{n_k}.
  \label{perf-test:eq:multinomial-ll}
\end{align}
\begin{figure}
\includegraphics[width=\textwidth]{cis-perfect-testing/regions_diag}
\caption[Admissible, inadmissible, and undetected regions]{%
  The regions for individual $i$.
  $i$'s first test was at time 0 and negative, with subsequent negative tests at times 7, 14, and 56, and positive tests at times 21 and 28.
  Inadmissible regions are unshaded.
  The grey (impossible) region covers the cases in which recovery occurs prior to infection.
  \label{perf-test:fig:partitionSpace}
}
\end{figure}

>>>>

Let $n_k$ denote the number of observations of $\vec{\nu}_k$; $\nnodet$ denote the latent number of undetected episodes; and $\vec{n} = [n_1, \dots, n_{N_D}, \nnodet]^T$.
Hence, $\ntot = \sum_{i=1}^{N_D} n_i + \nnodet$.
For $\vec{\nu}_k \in \set{E}$, let $p_k = \prob(O(j) = \vec{\nu}_k \mid \vec{\theta})$; $p_u = \prob(O(j) = \emptyset \mid \vec{\theta})$; and $\vec{p} = [p_1, \dots, p_D, p_u]^T$.
Assume, for tractability, that the events $O(j) = \vec{\nu}_k$ and $O(j') = \vec{\nu}_{k'}$ are independent for $j \neq j'$; this assumption is discussed in \cref{perf-test:sec:discussion}.
Then:
\begin{align}
  \vec{n} \mid \ntot, \vec{\theta} &\dist \MN(\ntot, \vec{p})
\intertext{that is:}
  p(\vec{n} \mid \ntot, \vec{\theta}) &= \frac{\ntot!}{\nnodet!\prod_{k=1}^{N_D} n_k!} p_u^{\nnodet} \prod_{k=1}^{N_D} p_k^{n_k}.
  \label{perf-test:eq:multinomial-ll}
\end{align}
\begin{figure}
\makebox[\textwidth][c]{\includegraphics[width=0.9\paperwidth]{cis-perfect-testing/regions_diag}}
\thisfloatpagestyle{empty}
\caption[Episode regions]{%
  Each dot is a combination of $b_j$ and $e_j$ for an arbitrary individual $i$.
  Each box, bounded by dashed lines, are combinations giving $O(j) = \nu_k$, $k$ corresponding to the numeric label; labels are arbitrary but unique across all individuals.

  $i$ had negative tests at times 0, 7, 14, 56, and 84 (not shown) and positive tests at times 21 and 28.

  The purple region corresponds to the doubly interval censored episode in this individual.
  That is, $n_8 = 1$ and $n_k = 0$ for $k = 1, \dots, 7, 9, \dots, 15$.

  The red region corresponds to combinations giving $O(j) = \emptyset$.

  Impossible region violates $b_j \leq e_j$.
}
\label{perf-test:fig:partitionSpace}
\end{figure}
